\documentclass[10pt, letterpaper]{article}

% Packages:
\usepackage[
    ignoreheadfoot,
    top=2 cm,
    bottom=2 cm,
    left=2 cm,
    right=2 cm,
    footskip=1.0 cm
]{geometry}
\usepackage[explicit]{titlesec}
\usepackage{tabularx}
\usepackage{wasysym} % for smiley and other symbols
\usepackage{array}
\usepackage[dvipsnames]{xcolor}
\definecolor{primaryColor}{RGB}{0, 79, 144}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{amsmath}
\usepackage[
    pdftitle={Chunxu Han - CV},
    pdfauthor={Chunxu Han},
    pdfcreator={LaTeX},
    colorlinks=true,
    urlcolor=primaryColor
]{hyperref}
\usepackage[pscoord]{eso-pic}
\usepackage{calc}
\usepackage{bookmark}
\usepackage{lastpage}
\usepackage{changepage}
\usepackage{paracol}
\usepackage{ifthen}
\usepackage{needspace}
\usepackage{iftex}
\usepackage{multicol}
\usepackage{datetime2}

% Ensure machine-readable PDF:
\ifPDFTeX
  \input{glyphtounicode}
  \pdfgentounicode=1
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{lmodern}
\fi

\usepackage[default, type1]{sourcesanspro}

% Layout tweaks:
\AtBeginEnvironment{adjustwidth}{\partopsep0pt}
\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\topskip}{0pt}
\setlength{\columnsep}{0.15cm}
\makeatletter
\let\ps@customFooterStyle\ps@plain
\patchcmd{\ps@customFooterStyle}{\thepage}{
    \color{gray}\textit{\small Chunxu Han}
}{}{}
\makeatother
\pagestyle{customFooterStyle}

\titleformat{\section}{
    \needspace{4\baselineskip}
    \Large\color{primaryColor}
}{}{
}{
    \textbf{#1}\hspace{0.15cm}\titlerule[0.8pt]\hspace{-0.1cm}
}[]

\titlespacing{\section}{-1pt}{0.25 cm}{0.15 cm}

\newenvironment{highlights}{
    \begin{itemize}[
        topsep=0.08 cm,
        parsep=0.08 cm,
        partopsep=0pt,
        itemsep=0pt,
        leftmargin=0.4 cm + 10pt
    ]
}{
    \end{itemize}
}

\newenvironment{onecolentry}{
    \begin{adjustwidth}{0.2 cm}{0.2 cm}
}{
    \end{adjustwidth}
}

\newenvironment{twocolentry}[2][]{
    \onecolentry
    \def\secondColumn{#2}
    \setcolumnwidth{\fill, 4.5 cm}
    \begin{paracol}{2}
}{
    \switchcolumn \raggedleft \secondColumn
    \end{paracol}
    \endonecolentry
}

\newenvironment{header}{
    \setlength{\topsep}{0pt}\par\kern\topsep\centering\color{primaryColor}\linespread{1.35}
}{
    \par\kern\topsep
}

\let\hrefWithoutArrow\href
\renewcommand{\href}[2]{\hrefWithoutArrow{#1}{\ifthenelse{\equal{#2}{}}{ }{#2 }\raisebox{.15ex}{\footnotesize \faExternalLink*}}}

\begin{document}
    \newcommand{\AND}{\unskip
        \cleaders\copy\ANDbox\hskip\wd\ANDbox
        \ignorespaces
    }
    \newsavebox\ANDbox
    \sbox\ANDbox{}

    % ---------- Header ----------
    \begin{header}
        \raggedright
        \fontsize{26 pt}{26 pt} 
        \textbf{Chunxu Han}

        \vspace{0.28 cm}

        \normalsize
        \mbox{{\footnotesize\faMapMarker*}\hspace*{0.13cm}Peder Skrams Gade 16A, København K}%
        \kern 0.25 cm%
        \AND%
        \kern 0.25 cm%
        \mbox{\hrefWithoutArrow{mailto:s220311@dtu.dk}{{\footnotesize\faEnvelope[regular]}\hspace*{0.13cm}s220311@dtu.dk}}%
        \kern 0.25 cm%
        \AND%
        \kern 0.25 cm%
        \mbox{\hrefWithoutArrow{tel:+45 52 73 06 85}{{\footnotesize\faPhone*}\hspace*{0.13cm}+45 52 73 06 85}}%
        \kern 0.25 cm%
        \AND%
        \kern 0.25 cm%
        \mbox{\hrefWithoutArrow{https://www.linkedin.com/in/chunxu-han/}{{\footnotesize\faLinkedinIn}\hspace*{0.13cm}chunxu-han}}%
    \end{header}

    \vspace{0.25 cm}

    % ---------- Profile ----------
    \section{Motivation}
    \begin{onecolentry}
        I’m a big fan of bubble tea and used to drink it almost every day when I lived in China. While studying in Beijing, I often helped my friend at her university coffee shop, where I really enjoyed preparing drinks, talking with customers, and creating a welcoming atmosphere. I also ran a small shop at Sino-Danish College, where I was responsible for daily operations, stock management, and customer service. I feel this position fits my interests and experience very well. I’m flexible with working hours and live nearby, and I’d be very happy to join the Sober Boba team.
    \end{onecolentry}

    % ---------- Strengths ----------
    \section{Selected Strengths}
    \begin{onecolentry}
        \begin{highlights}
    \item \textbf{Bubble Tea Interest:} I always keep track of milk tea trends on social media and am willing to learn and try new products.
    \item \textbf{Hospitality \& service mindset:} Naturally attentive and positive in every interaction. I enjoy making guests feel welcome, seen, and at ease.
    \item \textbf{Adaptable \& organised:} Used to fast-paced environments from managing a student store. I can handle multiple tasks while maintaining focus on quality and details.
    \item \textbf{Team player:} I'm reliable and supportive. I collaborate easily with others and enjoy being part of a friendly and motivated team.
    \item \textbf{SoMe:} Active on social media and aware of how digital presence strengthens retail visibility. Experienced in social media listening and trend tracking for clients. Interested in contributing ideas to strengthen Sober Boba’s online presence.
    \item \textbf{Languages:} English (proficient, IELTS 7.0), Chinese (native), Danish (basic, learning).
\end{highlights}
    \end{onecolentry}

    % ---------- Experience ----------
    \section{Experience}

    \begin{twocolentry}{
        Beijing, China\\
        Sep 2021 -- Sep 2022
    }
        \textbf{Shop Owner \& Manager}; Sino–Danish College (SDC)
        \begin{highlights}
            \item Placed supplier orders online, received and checked deliveries.
            \item Organised warehouse, tracked expiry dates and rotated stock.
            \item Restocked shelves daily, updated price tags and simple displays.
            \item Collected customer feedback and handled returns/claims with suppliers.
            \item Developed \textbf{logistics, multitasking, and problem–solving} in a fast mini–retail setting.
        \end{highlights}
    \end{twocolentry}

    \vspace{0.18 cm}

    \begin{twocolentry}{
        Lyngby, Denmark\\
        Oct 2023 -- Jul 2025
    }
        \textbf{Research Assistant}, DTU HealthTech
        \begin{highlights}
            \item Supported colleagues daily with \textbf{clear communication} and reliable follow–up.
            \item High attention to details and \textbf{quality mindset} in documentation and tasks.
        \end{highlights}
    \end{twocolentry}

    \vspace{0.18 cm}

    \begin{twocolentry}{
        Shanghai, China\\
        Feb 2023 -- May 2023
    }
        \textbf{Consulting Intern}, Illuminera (IQVIA)
        \begin{highlights}
            \item As a \textbf{Client–facing} work, I listened, asked good questions and prepared clean deliverables.
            \item Performed \textbf{social media listening and monitoring} to provide clients with up-to-date market trends and bring new insights.
        \end{highlights}
    \end{twocolentry}

    % % ---------- Education ----------
    % \section{Education}
    % \begin{twocolentry}{
    %     Lyngby, Denmark\\
    %     Sep 2023 -- Present
    % }
    %     \textbf{MSc, Bioinformatics \& Systems Biology} — Technical University of Denmark (DTU)
    %     \begin{highlights}
    %         \item Developed a structured, detail–oriented and collaborative way of working.
    %     \end{highlights}
    % \end{twocolentry}

    % \vspace{0.15 cm}

    % \begin{twocolentry}{
    %     Beijing, China\\
    %     Sep 2017 -- Jun 2021
    % }
    %     \textbf{BSc, Biotechnology} — Beijing Normal University
    % \end{twocolentry}

    % ---------- Extras ----------
    \section{Additional}
    \begin{onecolentry}
        \textbf{Interests:} I’ve been playing \textbf{badminton} since an early age—it’s a hobby that keeps me focused and energised. I also love \textbf{hiking}, both for the chance to connect with nature and for the challenge of seeing hidden scenery that isn’t easily accessible. After moving to Copenhagen, I developed a new passion for exploring \textbf{nordic design stores}, and I already have a few pieces on my wish list waiting to buy after graduation~\smiley{}.\\
        % \textbf{Availability:} I’m currently writing my master’s thesis and live within walking distance of ILLUM, so I’m quite flexible for a part-time job, both on weekdays, weekends, and during holiday seasons.
    \end{onecolentry}

\end{document}